Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2024-04-20 revision-1/model.tex
checkpoint

Given inputs $\store$ and ideal
functionality output $v$, we write $ \prob(\SIM(\store,v) = \store') $
to denote the probability that $\SIM(\store,v)$ returns corrupt views
$\store'$ as a result. We can then define the probability distribution
of corrupt views reconstructed by the simulator as follows:
\begin{definition}
  Given $C$, $\store$, and $v$, we write $\dist(\SIM(\store,v))$ to
  denote the distribution of corrupt views reconstructed by the
  simulation, where for
  all $\store' \in \mems(V)$:
  $$
  \dist(\SIM(\store,v))(\store')\ \defeq\ \prob(\SIM(\store,v) = \store') 
  $$
\end{definition}
Then we can define passive security in the real/ideal
model as follows. 
\begin{definition}[Passive Security]
  Assume given a program $\prog$ that correctly implements an ideal
  functionality $\idealf$, with $\views(\prog) = V$.  Then $\prog$
  is \emph{passive secure in the simulator model} iff for all
  partitions of the federation into honest and corrupt sets $H$ and $C$
  and for all $\store \in \mems(S)$ there exists a
  simulation $\SIM$ such that:
  $$
  \dist(\SIM(\store_{C},\idealf(\store))) = \condd{\progtt(\prog)}{\houtputs}{\store}
  $$
\end{definition}

>>>>

Given inputs $\store$ and ideal
functionality output $v$, we write $ \prob(\SIM(\store,v) = \store') $
to denote the probability that $\SIM(\store,v)$ returns corrupt views
$\store'$ as a result. We can then define the probability distribution
of corrupt views reconstructed by the simulator as follows:
\begin{definition}
  Given $C$, $\store$, and $v$, we write $\dist(\SIM(\store,v))$ to
  denote the distribution of corrupt views reconstructed by the
  simulation, where for
  all $\store' \in \mems(V)$:
  $$
  \dist(\SIM(\store,v))(\store')\ \defeq\ \prob(\SIM(\store,v) = \store') 
  $$
\end{definition}
Then we can define passive security in the real/ideal
model as follows. 
\begin{definition}[Passive Security]
  Assume given a program $\prog$ that correctly implements an ideal
  functionality $\idealf$, with $\views(\prog) = V$.  Then $\prog$
  is \emph{passive secure in the simulator model} iff for all
  partitions of the federation into honest and corrupt sets $H$ and $C$
  and for all $\store \in \mems(S)$ there exists a
  simulation $\SIM$ such that:
  $$
  \dist(\SIM(\store_{C},\idealf(\store))) = \condd{\progtt(\prog)}{\houtputs}{\store}
  $$
\end{definition}
Observe that this definition relies on protocol correctness, which
we can define as follows.
\begin{definition}[Passive Correctness]
  Given $\prog$ with output variables $\out{1},\ldots,\out{n}$ and ideal
  functionality $\idealf$, we say that $\prog$ is \emph{passive correct}
  for $\idealf$ iff for all $\store \in \mems(\secrets(\prog))$
  with $\idealf(\store) = v_1,\ldots,v_n$ we have
  $\progtt(\prog)(\out{1} \mapsto v_1,\ldots,\out{n} \mapsto v_n \mid \store) = 1$.
\end{definition}
